Models of gravitational lens candidates from Space Warps CFHTLS

### 2017-08-24 parts/stelmass.tex
replace total mass with lensing mass
replace total mass with lensing mass 2

Figure~\ref{fig:stelmass} shows a comparison of stellar and total
masses.  The comparatively large span in the stellar mass shows the range 
between the masses derived using the two age trends respectively.
It will 
be improved in future work by using available optical and NIR
magnitudes to derive more accurate constraints on the stellar
populations.

@@

Figure~\ref{fig:stelmass} shows most of the candidates having stellar
and total mass typical of massive ellipticals.  SW05 is one of the
most massive of all the candidates, with a mass of galaxy-group scale.
It is a particularly attractive system for follow-up observations at
higher resolution, as it is a large system with clear multiple-image
features, and modelling leaves little doubt that it is a lens.  SW04
seems to be even more massive, but the diagnostics leave some doubts
about this model.  The two lowest-mass systems, SW19 and SW42, are
important if they are indeed lenses, as they would be low-mass lenses
dominated by dark matter.  All the modelled systems have reasonable
stellar-mass fractions, except for two cases where the stellar-mass
fraction is too low (halo-matching index $>1$): these are SW42 and
SW57.  In the case of SW57, the model has poor diagnostics and should
be discounted.  The model for SW42, on the other hand, is quite
convincing --- except for the high halo-matching index.  If SW42 turns
out not to be a lens, that would support the halo-matching index as an
effective criterion for filtering models.

>>>>

Figure~\ref{fig:stelmass} shows a comparison of stellar and lensing
masses.  The comparatively large span in the stellar mass shows the range 
between the masses derived using the two age trends respectively.
It will 
be improved in future work by using available optical and NIR
magnitudes to derive more accurate constraints on the stellar
populations.

@@

Figure~\ref{fig:stelmass} shows most of the candidates having stellar
and lensing mass typical of massive ellipticals.  SW05 is one of the
most massive of all the candidates, with a mass of galaxy-group scale.
It is a particularly attractive system for follow-up observations at
higher resolution, as it is a large system with clear multiple-image
features, and modelling leaves little doubt that it is a lens.  SW04
seems to be even more massive, but the diagnostics leave some doubts
about this model.  The two lowest-mass systems, SW19 and SW42, are
important if they are indeed lenses, as they would be low-mass lenses
dominated by dark matter.  All the modelled systems have reasonable
stellar-mass fractions, except for two cases where the stellar-mass
fraction is too low (halo-matching index $>1$): these are SW42 and
SW57.  In the case of SW57, the model has poor diagnostics and should
be discounted.  The model for SW42, on the other hand, is quite
convincing --- except for the high halo-matching index.  If SW42 turns
out not to be a lens, that would support the halo-matching index as an
effective criterion for filtering models.

### 2017-08-24 parts/summary.tex
replace total mass with lensing mass 2

The trend in Figure~\ref{fig:stelmass}, that higher-mass galaxies get
progressively more dark-matter dominated, is expected,
e.g. see \cite{2005ApJ...623L...5F}, as is the span of about one order
of magnitude for the stellar mass and the two order of magnitudes for the total
mass.
With future data, it would be interesting to compare enclosed
stellar and total mass as a function of radius, going from
star-dominated inner regions to dark halos.
\cite{2011ApJ...740...97L} illustrate this behaviour in their
Figure~5, but the present sample could go an order of magnitude higher
in mass.

>>>>

The trend in Figure~\ref{fig:stelmass}, that higher-mass galaxies get 
progressively more dark-matter dominated, is expected, e.g. see 
\cite{2005ApJ...623L...5F}, as is the span of about one order of magnitude for 
the stellar mass and the two order of magnitudes for the lensing mass. With 
future data, it would be interesting to compare enclosed stellar and lensing 
mass as a function of radius, going from star-dominated inner regions to dark 
halos. \cite{2011ApJ...740...97L} illustrate this behaviour in their Figure~5, 
but the present sample could go an order of magnitude higher in mass.
